Technical Report

### 2017-10-19 fully-abstract-comp/technical-report.tex
Added some VERY preliminary LR definitions along with comments here and there. The value relation is still missing entirely and some of the other definitions do not 'fit' together.

@@

@@

%%% Operational semantics
\newcommand{\step}{\rightarrow}
\newcommand{\nstep}[1][n]{\step_{#1}}
\newcommand{\steps}{\step^*}
\newcommand{\diverge}{\Uparrow}

@@

\noindent\textbf{call}\\
\lau{19-09-2017: How do we get the $\sigma_?$ for the return pointers? It should be in memory somewhere.}
\lau{19-09-2017: In which cases do we have undefined here?}
This instruction assumes that the current address of the stack pointer, $\aaddr_\stk$, points to the first free address of the stack. We assume a seal assignment function $\sealAss{}$ that given an address assigns a seal.\lau{25-09-2017: This will need some more explanation - namely, there should be some relationship between the available seals and this function (I also need to think more about the specifics of this).}
\begin{align*}
  \sem{\scall{\src{r_1}}{\src{r_2}}}(\Phi) = & 
                                               \begin{cases}
                                                 \Phi'
                                                 \arraycolsep=0pt
                                                 \begin{array}[t]{rl}
                                                   &\updReg{r_1}{w_1} \\
                                                        &\updReg{r_2}{w_2} \\
                                                        &\updReg{\pcreg}{c_1}\\
                                                        &\updReg{\rdata}{c_2}\\
                                                        &\updReg{\rstk}{c_\stk}\\
                                                        &\updReg{r_{\var{ret,c}}}{\retptrc(\sigma_?)}\\
                                                        &\updReg{r_{\var{ret,d}}}{\retptrd(\sigma_?)}
                                                 \end{array}
                                                 & 
                                                 \arraycolsep=0pt
                                                 \begin{array}[t]{l}
                                                   \Phi(r_1) = \sealed{c_1,\sigma_1} \tand \\
                                                   \Phi(r_2) = \sealed{c_2,\sigma_2} \tand \\
                                                   \sigma_1 = \sigma_2 \tand \\
                                                   \nonExec{c_2} \tand\\
                                                   \Phi = (\mem,\reg,\stk,\ms_\stk) \tand\\
                                                   \Phi(\rstk) = \stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk} \tand \\
                                                   \baddr_\stk < \aaddr_\stk \leq \eaddr_\stk \tand \\
                                                   \ms_{\stk,\priv} = \ms_\stk |_{[\aaddr_\stk,\eaddr]}\update{\aaddr_\stk}{\eaddr_\stk} \tand\\
                                                   \ms_{\stk,\var{rest}} = \ms_\stk|_{[\baddr_\stk,\aaddr_\stk - 1]} \tand \\
                                                   c_\stk = \stkptr{\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1} \tand \\
                                                   \Phi(\pcreg) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                                   \opc = ((\perm,\lin),\baddr,\eaddr,\aaddr+\calllen) \tand \\
                                                   \stk' = (\opc,\ms_{\stk,\priv},\aaddr_\stk) :: \stk \tand\\
                                                   \Phi' = (\mem,\reg,\stk',\ms_{\stk,\var{rest}})\tand\\
                                                   \mem(\baddr) = \seal{\_,\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}\tand\\
                                                   \sigma_\baddr \leq \sigma_? \leq \sigma_\eaddr \tand\\
                                                   \sigma_? = \sealAss{a} \tand\\
                                                   w_1 = \linCons{\Phi(r_1)} \tand \\
                                                   w_2 = \linCons{\Phi(r_2)}
                                                 \end{array}
                                               \end{cases}
\end{align*}

@@

\clearpage
\section{Full Abstraction}
\begin{definition}
  \label{def:points-to-instr}
  A configuration $(\ms,\reg)$ {\sourcecolor or $(\ms,\reg,\_,\_)$} is said to point instruction $i$ in $A$ iff
  \[
    \reg(\pcreg) = ((\_,\_),\_,\_,\aaddr) \tand \aaddr \in A
  \]
and
\[
  \decInstr{\ms(\aaddr)} = i
\]
\end{definition}

>>>>

\newcommand{\npair}[2][n]{\left(#1,#2\right)}

@@

%%% Logical Relation notation
\newcommand{\typesetlr}[1]{\mathcal{#1}}
\newcommand{\lre}{\typesetlr{E}}
\newcommand{\lrk}{\typesetlr{K}}
\newcommand{\lrr}{\typesetlr{R}}
\newcommand{\lro}{\typesetlr{O}}
\newcommand{\lrv}{\typesetlr{V}}

\newcommand{\stpair}[3][]{
\ifthenelse{\equal{#1}{}}
{\left(\src{#2}_S,#3_T\right)}
{\left(\src{#2},#3\right)}}

\newcommand{\memSat}[4][n]{#2 :_{#1}^{#3}#4}

\newcommand{\World}{\mathrm{World}}

\newcommand{\future}{\sqsupseteq}
\newcommand{\privft}{\future^{\mathrm{priv}}}
\newcommand{\pubft}{\future^{\mathrm{pub}}}

@@

%%% Operational semantics
\newcommand{\step}{\rightarrow}
\newcommand{\nstep}[1][n]{\step_{#1}}
\newcommand{\steps}{\step^*}
\newcommand{\diverge}{\Uparrow}
\newcommand{\term}[1][-]{\Downarrow}

@@

\noindent\textbf{call}\\
\lau{19-09-2017: How do we get the $\sigma_?$ for the return pointers? It should be in memory somewhere.}
\lau{19-09-2017: In which cases do we have undefined here?}
This instruction assumes that the current address of the stack pointer, $\aaddr_\stk$, points to the first free address of the stack. We assume a seal assignment function $\sealAss{}$ that given an address assigns a seal.\lau{25-09-2017: This will need some more explanation - namely, there should be some relationship between the available seals and this function (I also need to think more about the specifics of this).}
\begin{align*}
  \sem{\scall{\src{r_1}}{\src{r_2}}}(\Phi) = & 
                                               \begin{cases}
                                                 \Phi'
                                                 \arraycolsep=0pt
                                                 \begin{array}[t]{rl}
                                                   &\updReg{r_1}{w_1} \\
                                                        &\updReg{r_2}{w_2} \\
                                                        &\updReg{\pcreg}{c_1}\\
                                                        &\updReg{\rdata}{c_2}\\
                                                        &\updReg{\rstk}{c_\stk}\\
                                                        &\updReg{\rretc}{\retptrc(\sigma_?)}\\
                                                        &\updReg{\rretd}{\retptrd(\sigma_?)}
                                                 \end{array}
                                                 & 
                                                 \arraycolsep=0pt
                                                 \begin{array}[t]{l}
                                                   \Phi(r_1) = \sealed{c_1,\sigma_1} \tand \\
                                                   \Phi(r_2) = \sealed{c_2,\sigma_2} \tand \\
                                                   \sigma_1 = \sigma_2 \tand \\
                                                   \nonExec{c_2} \tand\\
                                                   \Phi = (\mem,\reg,\stk,\ms_\stk) \tand\\
                                                   \Phi(\rstk) = \stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk} \tand \\
                                                   \baddr_\stk < \aaddr_\stk \leq \eaddr_\stk \tand \\
                                                   \ms_{\stk,\priv} = \ms_\stk |_{[\aaddr_\stk,\eaddr]}\update{\aaddr_\stk}{\eaddr_\stk} \tand\\
                                                   \ms_{\stk,\var{rest}} = \ms_\stk|_{[\baddr_\stk,\aaddr_\stk - 1]} \tand \\
                                                   c_\stk = \stkptr{\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1} \tand \\
                                                   \Phi(\pcreg) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                                   \opc = ((\perm,\lin),\baddr,\eaddr,\aaddr+\calllen) \tand \\
                                                   \stk' = (\opc,\ms_{\stk,\priv},\aaddr_\stk) :: \stk \tand\\
                                                   \Phi' = (\mem,\reg,\stk',\ms_{\stk,\var{rest}})\tand\\
                                                   \mem(\baddr) = \seal{\_,\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}\tand\\
                                                   \sigma_\baddr \leq \sigma_? \leq \sigma_\eaddr \tand\\
                                                   \sigma_? = \sealAss{a} \tand\\
                                                   w_1 = \linCons{\Phi(r_1)} \tand \\
                                                   w_2 = \linCons{\Phi(r_2)}
                                                 \end{array}
                                               \end{cases}
\end{align*}

@@

\clearpage

\section{Logical Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\lau{19-10-2017: Maybe linearity should be taken care of in just one place (instead of in $\lrr$ relation and mem staisfaction). That is, add a predicate that checks whether the configuration satisfies linearity (such a condition may be to syntactic to work?).}
\[
  \lre(W) = \left\{ \npair{\stpair{v}{v}} \middle| 
    \begin{array}{l}
      \forall n' \leq n \ldotp \\
      \quad \forall \npair[n']{\stpair[.]{(k_{d,S},k_{c,S})}{(k_{d,T},k_{c,T})}} \in \lrk(W) \ldotp \\
      \qquad \forall \stpair{\reg}{\reg}\ldotp \npair[n']{
      \left(\array{l}\src{\reg_S\updReg{\pcreg,\rretd,\rretc}{v_S,k_{d,S},k_{c,S}}},\\\reg_T\updReg{\pcreg,\rretd,\rretc}{v_T,k_{d,T},k_{c,T}}\endarray\right)} \in \lrr(W) \Rightarrow\\
      \qquad \quad \forall \src{\ms_S},\ms_T \ldotp \memSat[n']{\stpair[.]{\ms}{\ms}}{\stpair{\reg}{\reg}}{W} \Rightarrow \\
      \qquad \qquad \npair[n']{\left(\array{l}\src{(\reg_S\updReg{\pcreg}{v_S}\updReg{r_\ret}{k_V},\ms_S)},\\(\reg_T\updReg{\pcreg}{v_T}\updReg{r_\ret}{k_T},\ms_T)\endarray\right)}
      \in \lro(W)
    \end{array}
            \right\}
\]

\[
  \lro(W) = \left\{ \npair{\stpair[.]{(\reg_S,\ms_S,\stk_S,\ms_{\stk,S})}{\reg_R,\ms_R}} \middle|
    \begin{array}{l}
      \forall i \leq n, \stpair{\mem}{\mem} \ldotp \\
      \quad \src{(\reg_S,\ms_S \cup \mem_S,\stk_S,\ms_{\stk,S})} \term[i] \Rightarrow (\reg_R,\ms_R) \term\\
      \quad tand\\
      \quad (\reg_R,\ms_R) \term[i] \Rightarrow \src{(\reg_S,\ms_S \cup \mem_S,\stk_S,\ms_{\stk,S})} \term
    \end{array}
\right\}
\]

\lau{19-10-2017: $\lrk$ may indicate that $\lre$ should really be a relation between a \src{source pc} and a pair of a target pc and stack pointer? Otherwise, what happens with the data part of the return pointer?}
\[
  \lrk(W) = \left\{ \npair{\stpair[.]{\retptrd{\sigma},\retptrc{\sigma}}{k_{d,T},k_{c,T}}} \middle|
    \begin{array}{l}
      k_{d,T} \text{ is a stack pointer with correct end and such with everything related to the source stack} \\
      k_{c,T} \text{ relates to the old pc on the stack}\\
      \forall n' \leq n \ldotp \\
      \quad \forall W' \privft W \ldotp \\
      \qquad \dots \in \lre(W')
    \end{array}
            \right\}
\]

\[
  \lrr(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : \RegName \fun \World \ldotp \\
      \quad S \text{ is a separation of $W$} \tand
      \quad \forall r \in \dom(\reg_T) \setminus \{\pcreg, \rretd,\rretc \}\ldotp
      \npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
Where $S\text{ is a separation of $W$}$ means that no two partion share the same ``pure'' region (whatever that is).

\[
  \lrv(W) = \left\{ \dots \right\}
\]

\section{Full Abstraction}
\begin{definition}
  \label{def:points-to-instr}
  A configuration $(\ms,\reg)$ {\sourcecolor or $(\ms,\reg,\_,\_)$} is said to point instruction $i$ in $A$ iff
  \[
    \reg(\pcreg) = ((\_,\_),\_,\_,\aaddr) \tand \aaddr \in A
  \]
and
\[
  \decInstr{\ms(\aaddr)} = i
\]
\end{definition}
